Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-04-30 analysis/paper/asymsam.Rmd
Agrega comentario de detrend
#17
Cambio menor y render.

To assess differences in the impacts associated with the SAM, A\nobreakdash-SAM and S\nobreakdash-SAM indices we regressed surface land air and sea temperature and precipitation onto each of the three SAM indices at 700 hPa.
As shown in previous sections, the three indices are highly coherent in the troposphere, so we select this level to represent the tropospheric circulation for consistency with previous studies.

@@

All data used in this paper is freely available from their respective sources.
ERA5 data can be obtained via the Copernicus Climate Data Store ([\<https://cds.climate.copernicus.eu/cdsapp\#!/dataset/reanalysis-era5-pressure-levels-monthly-means\>](https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means){.uri}).
CMAP Precipitation data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at <https://psl.noaa.gov/data/gridded/data.cmap.html>.
The Oceanic Niño Index is available via NOAA's Climate Prediction Center: <https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt>
The SAM, A\nobreakdash-SAM and S\nobreakdash-SAM indices are available at the public repository associated with this paper, at <https://github.com/eliocamp/asymsam/tree/main/analysis/data/derived_data>.

>>>>

To assess differences in the impacts associated with the SAM, A\nobreakdash-SAM and S\nobreakdash-SAM indices we regressed surface land air and sea temperature and precipitation onto each of the three SAM indices at 700 hPa.
As shown in previous sections, the three indices are highly coherent in the troposphere, so we select this level to represent the tropospheric circulation for consistency with previous studies.
Regressions were done without detrending either the variables nor the indices, but computing the regressions with detrended values doesn't change the results (not shown).

@@

All data used in this paper is freely available from their respective sources.
ERA5 data can be obtained via the Copernicus Climate Data Store ([\<https://cds.climate.copernicus.eu/cdsapp\#!/dataset/reanalysis-era5-pressure-levels-monthly-means\>](https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-pressure-levels-monthly-means){.uri}).
CMAP Precipitation data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at <https://psl.noaa.gov/data/gridded/data.cmap.html>.
The Oceanic Niño Index is available via NOAA's Climate Prediction Center: <https://www.cpc.ncep.noaa.gov/products/analysis_monitoring/ensostuff/detrend.nino34.ascii.txt>
The SAM, A\nobreakdash-SAM and S\nobreakdash-SAM indices are available at the public repository associated with this paper, at <https://github.com/eliocamp/asymsam/tree/master/analysis/data/derived_data>.
